\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2013-12-28 doc/paper.tex
reformulate the pole-mass section a bit

\begin{figure}[tb]
  \centering
  \tikzumlset{fill class=white}
  \begin{tikzpicture}
    \umlclass[x=0, y=0, type=abstract]{Two\_scale\_model}{}{
      + \umlvirt{calculate\_spectrum() : void}\\
      + \umlvirt{run\_to(scale : double, eps : double) : void}\\
      + \umlvirt{set\_precision(precision : double) : void}
    }
    \umlclass[x=0, y=-4]{RGFlow$<$Two\_scale$>$}{}{
      + solve() : void
    }
    \umlclass[x=8, y=0]{Constraint$<$Two\_scale$>$}{}{
      + \umlvirt{apply() : void}\\
      + \umlvirt{get\_scale() : double}\\
      + \umlvirt{set\_model(model : Two\_scale\_model*) : void}
    }
    \umlclass[x=8, y=4, template={T}]{Constraint}{}{}
    \umlclass[x=0, y=-7]{Initial\_guesser$<$Two\_scale$>$}{}{
      + \umlvirt{guess() : void}
    }
    \umlclass[x=0, y=-11, template={T}]{Initial\_guesser}{}{}
    \umlclass[x=8, y=-7]{Convergence\_tester$<$Two\_scale$>$}{}{
      + \umlvirt{accuracy\_goal\_reached() : bool}\\
      + \umlvirt{max\_iterations() : unsigned}
    }
    \umlclass[x=8, y=-11, template={T}]{Convergence\_tester}{}{}
    \umlclass[x=8, y=-4, template={T}]{RGFlow}{}{}
    \umldep[arg1={$<<$bind$>>$}, mult1={T $\rightarrow$ Two\_scale}, pos1=0.5]{RGFlow$<$Two\_scale$>$}{RGFlow}
    \umldep[mult1=1..*]{RGFlow$<$Two\_scale$>$}{Two\_scale\_model}
    \umldep[mult1=1..*]{RGFlow$<$Two\_scale$>$}{Constraint$<$Two\_scale$>$}
    \umldep{RGFlow$<$Two\_scale$>$}{Initial\_guesser$<$Two\_scale$>$}
    \umldep{RGFlow$<$Two\_scale$>$}{Convergence\_tester$<$Two\_scale$>$}
    \umldep[mult1={$<<$bind$>>$}, arg1={T $\rightarrow$ Two\_scale}, pos1=0.5]{Initial\_guesser$<$Two\_scale$>$}{Initial\_guesser}
    \umldep[mult1={$<<$bind$>>$}, arg1={T $\rightarrow$ Two\_scale}, pos1=0.5]{Convergence\_tester$<$Two\_scale$>$}{Convergence\_tester}
    \umldep[arg1={$<<$bind$>>$}, mult1={T $\rightarrow$ Two\_scale}, pos1=0.5]{Constraint$<$Two\_scale$>$}{Constraint}
  \end{tikzpicture}
  \caption{Two-scale renormalization group solver class hierarchy}
  \label{fig:two-scale-rgflow-class-hierarchy}
\end{figure}
{\color{red} copied and pasted from latest manual -- not sure how best to maintain this, could split maual up into tiny bits, but we may also want some differences?}
\subsection{pole masses}
With the solver routine finished and convergence achieved, the $\overline{DR}$ parameters consistent with one loop EWSB, low energy data and all user supplied boundary conditions are then known at any scale between...

The physical mass spectrum can now be calculated.  \fs uses the full one-loop self energies and tree level routines to calculate the pole masses at the one-level.  If higher accuracy is required additional routines with higher order corrections can be added in a very simple way. For example in the MSSM by default \fs adds two loop Higgs FORTRAN routines supplied by P.~Slavich from \cite{slavich-degrassi} to add two loop corrections of $\oatas$, $\oabas$, $\oatq$, $\oabatau$, 
$\oabq$, $\oatauq$ and $\oatab$  as follows...  
Something similar is done for the NMSSM, but in this case the NMSSM $\oatas$, $\oabas$ pieces come from \cite{Degrassi:2009yq}, while for $\oatq$, $\oabatau$, 
$\oabq$, $\oatauq$ and $\oatab$ the MSSM pieces are used though it should be understood that these are not complete in the NMSSM. For other models since the Higgs mass is a very important measurement and the two loop corrections can be larger than the current experimental error \cite{Degrassi:2009yq} we recommend that the leading log two loop corrections are estimated, by generalising those of the MSSM or NMSSM, as has been done, for example, in the E$_6$SSM\cite{King:2005jy}.

>>>>

\begin{figure}[tb]
  \centering
  \tikzumlset{fill class=white}
  \begin{tikzpicture}
    \umlclass[x=0, y=0, type=abstract]{Two\_scale\_model}{}{
      + \umlvirt{calculate\_spectrum() : void}\\
      + \umlvirt{run\_to(scale : double, eps : double) : void}\\
      + \umlvirt{set\_precision(precision : double) : void}
    }
    \umlclass[x=0, y=-4]{RGFlow$<$Two\_scale$>$}{}{
      + solve() : void
    }
    \umlclass[x=8, y=0]{Constraint$<$Two\_scale$>$}{}{
      + \umlvirt{apply() : void}\\
      + \umlvirt{get\_scale() : double}\\
      + \umlvirt{set\_model(model : Two\_scale\_model*) : void}
    }
    \umlclass[x=8, y=4, template={T}]{Constraint}{}{}
    \umlclass[x=0, y=-7]{Initial\_guesser$<$Two\_scale$>$}{}{
      + \umlvirt{guess() : void}
    }
    \umlclass[x=0, y=-11, template={T}]{Initial\_guesser}{}{}
    \umlclass[x=8, y=-7]{Convergence\_tester$<$Two\_scale$>$}{}{
      + \umlvirt{accuracy\_goal\_reached() : bool}\\
      + \umlvirt{max\_iterations() : unsigned}
    }
    \umlclass[x=8, y=-11, template={T}]{Convergence\_tester}{}{}
    \umlclass[x=8, y=-4, template={T}]{RGFlow}{}{}
    \umldep[arg1={$<<$bind$>>$}, mult1={T $\rightarrow$ Two\_scale}, pos1=0.5]{RGFlow$<$Two\_scale$>$}{RGFlow}
    \umldep[mult1=1..*]{RGFlow$<$Two\_scale$>$}{Two\_scale\_model}
    \umldep[mult1=1..*]{RGFlow$<$Two\_scale$>$}{Constraint$<$Two\_scale$>$}
    \umldep{RGFlow$<$Two\_scale$>$}{Initial\_guesser$<$Two\_scale$>$}
    \umldep{RGFlow$<$Two\_scale$>$}{Convergence\_tester$<$Two\_scale$>$}
    \umldep[mult1={$<<$bind$>>$}, arg1={T $\rightarrow$ Two\_scale}, pos1=0.5]{Initial\_guesser$<$Two\_scale$>$}{Initial\_guesser}
    \umldep[mult1={$<<$bind$>>$}, arg1={T $\rightarrow$ Two\_scale}, pos1=0.5]{Convergence\_tester$<$Two\_scale$>$}{Convergence\_tester}
    \umldep[arg1={$<<$bind$>>$}, mult1={T $\rightarrow$ Two\_scale}, pos1=0.5]{Constraint$<$Two\_scale$>$}{Constraint}
  \end{tikzpicture}
  \caption{Two-scale renormalization group solver class hierarchy}
  \label{fig:two-scale-rgflow-class-hierarchy}
\end{figure}
{\color{red} copied and pasted from latest manual -- not sure how best to maintain this, could split maual up into tiny bits, but we may also want some differences?}

\subsection{Pole masses}
After the solver routine has finished and convergence has been
achieved, all $\overline{DR}$ parameters are consistent with the
one-loop EWSB conditions, low energy data and all user supplied
boundary conditions are known at any scale between \code{LowScale} and
\code{HighScale}.

The physical (pole) mass spectrum can now be calculated.  \fs uses the
full one-loop self-energies and tree-level mass matrices to calculate
the pole masses at the one-loop level.  If higher accuracy is required
additional routines with higher order corrections can be added in a
very simple way. For example in the MSSM by default \fs adds two-loop
Higgs FORTRAN routines supplied by P.~Slavich from
\cite{slavich-degrassi} to add two loop corrections of $\oatas$,
$\oabas$, $\oatq$, $\oabatau$, $\oabq$, $\oatauq$ and $\oatab$ as
follows... {\color{red} This is not yet implemented!}

Something similar is done for the NMSSM, but in this case the NMSSM
$\oatas$, $\oabas$ pieces come from \cite{Degrassi:2009yq}, while for
$\oatq$, $\oabatau$, $\oabq$, $\oatauq$ and $\oatab$ the MSSM pieces
are used though it should be understood that these are not complete in
the NMSSM. For other models since the Higgs mass is a very important
measurement and the two loop corrections can be larger than the
current experimental error \cite{Degrassi:2009yq} we recommend that
the leading log two loop corrections are estimated, by generalising
those of the MSSM or NMSSM, as has been done, for example, in the
E$_6$SSM\cite{King:2005jy}.  {\color{red} This is not yet implemented!}
